---
title: "HW 01 - My interest and two ways to visualize world development"
author: "Insert your name here"
format: 
  html: 
    code-fold: true
    embed-resources: true
    standalone: true
---

## My interest in visual communication and data storytelling

*Remove this text and write text for Exercise 1.*

## Hans Rosling's famous visualization

```{r}
#| label: load-packages-and-data
#| message: false
library(tidyverse)
library(gapminder)
```

*Remove this text for Exercise 2.*

This is a version of the graph which Hans Rosling used in his famous presentation about world development <https://www.youtube.com/watch?v=Z8t4k0Q8e8Y>. 

```{r}
#| label: rosling-visualization
#| fig.cap: GDP per capita vs. life expectancy from the gapminder data set as presented by Hans Rosling.
gapminder |> 
  filter(year == 1952 | year == 2007) |> 
  ggplot(mapping = aes(x = gdpPercap, 
                       y = lifeExp, 
                       color = continent, 
                       size = pop)) +
  geom_point() +
  facet_wrap(~year) +
  scale_x_log10(breaks = c(300,3000,30000))
```

## An alternative visualization 

Roland Paulsen copied the visualization and the presentation style in the video <https://youtu.be/OoIcsj9ysvs?t=31> (starting at 0:31). 

```{r}
#| label: paulsen-visualization
#| #| fig.cap: GDP per capita vs. life expectancy from the gapminder data set in the way of Roland Paulsen. 

# Remove this and put your code for Exercise 3
```


## What are the two different graphs emphasizing?

*Remove this text for Exercise 4.*